Web Authn Reference Implementation

### 2019-02-06 doc/paper/paper.tex
fixed some typos

\section{Replying Party Reference Implementation}
\label{sec:replying_party}

@@

\begin{figure}[h]
  \centering
  \begin{sequencediagram}
    \newthread{U}{User}{}
    \newinst[1]{T}{Token}{}
    \newinst[2.5]{B}{Browser}{}
    \newinst[3]{R}{Replying Party}{}
    \begin{call}{U}{Register}{B}{}
      \begin{call} {B}{/create(user)}{R}{makeCredentialJson}
      \end{call} 
      \begin{call} {B}{webAuthn.create}{T}{createResponse}
        \begin{call}{T}{activate}{U}{activation}
        \end{call}
      \end{call} 
      \begin{call} {B}{/response(createResponse)}{R}{username}
      \end{call} 
    \end{call}
  \end{sequencediagram}
  \caption{User Registration}
  \label{fig:user_registration}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{sequencediagram}
    \newthread{U}{User}{}
    \newinst[1]{T}{Token}{}
    \newinst[2.5]{B}{Browser}{}
    \newinst[3]{R}{Replying Party}{}
    \begin{call}{U}{Login}{B}{}
      \begin{call} {B}{/create(user)}{R}{createAuthenticationJson}
      \end{call} 
      \begin{call} {B}{webAuthn.get}{T}{authnResponse}
        \begin{call}{T}{activate}{U}{activation}
        \end{call}
      \end{call} 
      \begin{call} {B}{/response(authnResponse)}{R}{username}
      \end{call} 
    \end{call}
  \end{sequencediagram}
  \caption{User Authentication}
  \label{fig:user_authentication}
\end{figure}

@@

\lstinputlisting[language=json, caption=Attestation Response \gls{json}, label=lst:attestationResponse]{json/attestationResponse.json}

@@

\lstinputlisting[language=json, caption=Attestation Client Data \gls{json}, label=lst:attestationClientData]{json/attestationClientData.json}

>>>>

\section{Relying Party Reference Implementation}
\label{sec:replying_party}

@@

\begin{figure}[h]
  \centering
  \begin{sequencediagram}
    \newthread{U}{User}{}
    \newinst[1]{T}{Authenticator}{}
    \newinst[2.5]{B}{Browser}{}
    \newinst[3]{R}{\gls{rp}}{}
    \begin{call}{U}{Register}{B}{}
      \begin{call} {B}{/create(user)}{R}{makeCredentialJson}
      \end{call} 
      \begin{call} {B}{webAuthn.create}{T}{createResponse}
        \begin{call}{T}{activate}{U}{activation}
        \end{call}
      \end{call} 
      \begin{call} {B}{/response(createResponse)}{R}{username}
      \end{call} 
    \end{call}
  \end{sequencediagram}
  \caption{User Registration}
  \label{fig:user_registration}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{sequencediagram}
    \newthread{U}{User}{}
    \newinst[1]{T}{Authenticator}{}
    \newinst[2.5]{B}{Browser}{}
    \newinst[3]{R}{\gls{rp}}{}
    \begin{call}{U}{Login}{B}{}
      \begin{call} {B}{/create(user)}{R}{createAuthenticationJson}
      \end{call} 
      \begin{call} {B}{webAuthn.get}{T}{authnResponse}
        \begin{call}{T}{activate}{U}{activation}
        \end{call}
      \end{call} 
      \begin{call} {B}{/response(authnResponse)}{R}{username}
      \end{call} 
    \end{call}
  \end{sequencediagram}
  \caption{User Authentication}
  \label{fig:user_authentication}
\end{figure}

@@

\lstinputlisting[language=json, caption=Authentication Response \gls{json}, label=lst:attestationResponse]{json/attestationResponse.json}

@@

\lstinputlisting[language=json, caption=Authentication Client Data \gls{json}, label=lst:attestationClientData]{json/attestationClientData.json}
